Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-11 apples_and_oranges.qmd
Small things

######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
# A) the overall sample
# B) the CBT vs Fluox and Escitalopram sample
# C) the no WL sample

>>>>

######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
# A) the overall sample
# B) the CBT vs Fluox and Escitalopram sample
# C) the no WL sample
# D) the no WL or CAU sample
# E) the CDRS only sample
